Automated Reasoning of Relational properties using \\ Abstact Conflict Driven Clause Learning

### 2016-09-22 deductions.tex
deductions text updated

>>>>

Let us consider an example. 
int id(int a)
{
  return a;
}

void main() {
 int x,y,z;
 _Bool c;
 if (c)
   x = -1;
 else
   x = 2;
 int k = id(x);
 z = x * k;
 assert((z!=-2));
}

With forward iteration strategy using octagon domian, the program 
is proved without any decision. However, with the forward strategy
using interval domain, we just required one decision to prove the program.
